Text embedding models yield high-resolution insights into conceptual knowledge from short multiple-choice quizzes

### 2024-02-22 paper/main.tex
minor typo fix

To assess the predictive value of our knowledge estimates, we compared each
GLMM's ability to discriminate between correctly and incorrectly answered
questions to that of an analogous model that did \textit{not} consider estimated
knowledge. Specifically, we used the same sets of observations with which we
fit each ``full'' model to fit a second ``null'' model, with the formula:
\[
    \mathtt{accuracy \sim (1\ \vert\ participant) + (1\ \vert\ question)}
\]
where ``\texttt{accuracy}'', ``\texttt{participant}'', and ``\texttt{question}'' are as defined above. 
As with our full models, the null models we fit for the “All questions” version of the analysis for each quiz contained an additional term, $\mathtt{(1\ \vert\ lecture)}$, where ``\texttt{lecture}'' are as defined above. 
We then compared each full model to its reduced (null) equivalent using a likelihood-ratio test (LRT). 
Because the typical asymptotic $\chi^2_d$ approximation of the null distribution for the LRT statistic ($\lambda_{LR}$) is anti-conservative for models that differ in their random slope terms~\citep{GoldSimo00,ScheEtal08b,SnijBosk11}, we computed $p$-values for these tests using a parametric bootstrapping procedure~\citep{HaleHojs14}. 
For each of 1,000 bootstraps, we used the fitted null model to simulate a sample of observations of equal size to our original sample.
We then re-fit both the null and full models to this simulated sample and compared them via an LRT.
This yielded a distribution of $\lambda_{LR}$ statistics we may expect to observe under our null hypothesis.
Following~\citep{DaviHink97,NortEtal02}, we computed a corrected $p$-value for our observed $\lambda_{LR}$ as $\frac{r + 1}{n + 1}$, where $r$ is the number of simulated model comparisons that yielded a $\lambda_{LR}$ greater than or equal to our observed value and $n$ is the number of simulations we ran (1,000).

>>>>

To assess the predictive value of our knowledge estimates, we compared each
GLMM's ability to discriminate between correctly and incorrectly answered
questions to that of an analogous model that did \textit{not} consider estimated
knowledge. Specifically, we used the same sets of observations with which we
fit each ``full'' model to fit a second ``null'' model, with the formula:
\[
    \mathtt{accuracy \sim (1\ \vert\ participant) + (1\ \vert\ question)}
\]
where ``\texttt{accuracy}'', ``\texttt{participant}'', and ``\texttt{question}'' are as defined above. 
As with our full models, the null models we fit for the “All questions” version of the analysis for each quiz contained an additional term, $\mathtt{(1\ \vert\ lecture)}$, where ``\texttt{lecture}'' is as defined above. 
We then compared each full model to its reduced (null) equivalent using a likelihood-ratio test (LRT). 
Because the typical asymptotic $\chi^2_d$ approximation of the null distribution for the LRT statistic ($\lambda_{LR}$) is anti-conservative for models that differ in their random slope terms~\citep{GoldSimo00,ScheEtal08b,SnijBosk11}, we computed $p$-values for these tests using a parametric bootstrapping procedure~\citep{HaleHojs14}. 
For each of 1,000 bootstraps, we used the fitted null model to simulate a sample of observations of equal size to our original sample.
We then re-fit both the null and full models to this simulated sample and compared them via an LRT.
This yielded a distribution of $\lambda_{LR}$ statistics we may expect to observe under our null hypothesis.
Following~\citep{DaviHink97,NortEtal02}, we computed a corrected $p$-value for our observed $\lambda_{LR}$ as $\frac{r + 1}{n + 1}$, where $r$ is the number of simulated model comparisons that yielded a $\lambda_{LR}$ greater than or equal to our observed value and $n$ is the number of simulations we ran (1,000).
